R Notebook

### 2022-04-25 code/r/02_A_numeric_vs_hpo_for_liver_function.Rmd

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('.db_credential.R')
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), host='localhost', user=user, dbname = dbname, port = 2345, password=password)

# cache directory to read from or write to
CACHE_DIR <- './cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- FALSE
```

@@

ggsave(filename = 'cache/liver_labs_raw_data_distribution_by_rel_date.png', plot = p, width = 6, height = 6)
```

![liver function labs](./cache/liver_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(liver_analysis, file = 'cache/liver_analysis.csv', row.names = FALSE)

>>>>

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), 
                       host=Sys.getenv('DSCA_PHI_HOST'), 
                       dbname = Sys.getenv('DSCA_PHI_DBNAME'), 
                       port = Sys.getenv('DSCA_PHI_PORT'), 
                       user=Sys.getenv('DSCA_PHI_USERNAME'),
                       password= Sys.getenv('DSCA_PHI_PASSWORD'))

# cache directory to read from or write to
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- FALSE
```

@@

ggsave(filename = glue('{CACHE_DIR}/liver_labs_raw_data_distribution_by_rel_date.png', plot = p, width = 6, height = 6))
```

![liver function labs](./../../cache/liver_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(liver_analysis, file = glue('{CACHE_DIR}/liver_analysis.csv'), row.names = FALSE)

### 2022-04-25 code/r/02_B_numeric_vs_hpo_for_acute_kidney_failure.Rmd

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('.db_credential.R')
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), host='localhost', user=user, dbname = dbname, port = 2345, password=password)

# cache directory to read from or write to
CACHE_DIR <- './cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- TRUE
```

@@

Retrieve liver function diagnoses information for the cohort.
```{r}
sql <- "SELECT * FROM cohort"
df_cohort <- get_df_from_db_or_cache(cache_dir = CACHE_DIR, file_name = 'acute_kidney_failure_diagnoses.csv', db_access_callback = dbGetQuery, conn = dsca, statement = sql, force_rerun = FALSE)

>>>>

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), 
                       host=Sys.getenv('DSCA_PHI_HOST'), 
                       dbname = Sys.getenv('DSCA_PHI_DBNAME'), 
                       port = Sys.getenv('DSCA_PHI_PORT'), 
                       user=Sys.getenv('DSCA_PHI_USERNAME'),
                       password= Sys.getenv('DSCA_PHI_PASSWORD'))

# cache directory to read from or write to
CACHE_DIR = '../../cache'

if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- FALSE
```

@@

Retrieve liver function diagnoses information for the cohort.
```{r}
sql <- "SELECT * FROM cohort"
df_cohort <- get_df_from_db_or_cache(cache_dir = CACHE_DIR, file_name = 'acute_kidney_failure_diagnoses.csv', db_access_callback = dbGetQuery, conn = dsca, statement = sql, force_rerun = FORCE_RERUN)
